---
title: "Base R- Weekly Assignment #1"
author: "Christine Friendshuh"
date: "2022-09-28"
output: html_document
---

1. Name the four panels in R Studio and offer a brief description of each.

top left: this is where the files are, where we put anything we want to save.
top right: global environment. This contains everything we are working with, like variables, vectors, etc.
bottom left: console. This is where the output goes, can be used as scratch paper(nothing saved here), where you install.packages.
bottom right: everything else. You can see help files here.

2. Create a code chunk. Write your favorite number in it. 
```{r}
3
```

3. Add thirty-seven to six
```{r}
37 + 6
```

4. evaluate the following: six times four is equal to twenty-four
```{r}
6 * 4 == 24
```

5. What's the difference between an "and" and an "or" statement? 

For the "and" statement, both statements have to be true to output "true". For the "or" statement, either statement can be true to output "true".

6. Create an "and" statement for the following sentence: three is less than five and tree is the same as oak. 
```{r}
3 < 5 && "tree" == "oak"
```

7. Create a variable called "dinner" that contains your favorite thing to eat for dinner. 
```{r}
dinner<- "any takeout"
```

8. write out all numbers between 50 and 200
```{r}
50:200
```

9. print every odd number between 1 and 300. 

```{r}
seq(1,300,2)
```

10. repeat the phrase "i'm excited for fall" five times
```{r}
rep("I am excited for fall",5)

```


